Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex

### 2019-03-28 Manuscript.Rmd
Methods done. Onto Results

All network analyses were performed using the igraph package [@G.2006] in R 3.4.1 [@RTeam2018]. To establish each subject's network, we selected all the vertices contained within the mPFC/PCC search space (n = 4,801 per subject; mPFC = 2854, PCC = 1947) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them. Next, we applied Fisher's r to z transformation, and performed a two-sided significance test to identify strong correlations. The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were turned to 0 (all other edges retained their respective z-values). Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution. Values of 1 of this transformed distribution were returned to 0 in order to avoid the inclusion of these edges in the network analyses. We report the proportion of retained edges (i.e. network density) in the Results section. As part of the evaluation step, we produced these network weight matrices (and the community detection outlined below) at four levels: 1) for each run separately (1200 TRs each); 2) for the concatenated time series for the two runs on the same day (2400 TRs total); 3) for each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).

@@

Communities (i.e. clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2003]. First, each network was represented as an $n$ x $n$ network weight matrix (where $n$ = number of vertices within the ROIs, 4,801). This matrix was then transformed into its normalized Laplacian form

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlation values with every other vertex), and $W$ is the network weight matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. This transformation ensures that every row adds up to zero. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with [@Fiedler1975]. This method enforces the partition of a network into similarly-sized communities, and guarantees that they share at least one edge [@Chung1999]. In this way, spectral partitioning avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise). Every individual partition is therefore binarized by sign in order to evaluate the topography of each community (see next section for details). Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community to be the one containing the DMN-specific PCC parcel identified in our meta-analysis. The high density of these networks (see Results) ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].

In order to evaluate the convergent validity of the resulting partitions across community-detection methods, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al. [-@Clauset2004]. *(TBD) This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network. The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity.* Unlike SP, modularity can fractionate a network into more than two functional groups. We assumed that if the partitions from the bounded and unbounded community detection methods showed high levels of agreement, we could gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not. We also diagnosed our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by spectral partitioning to be non-zero. This eigenvalue serves as an estimator of the optimal number of communities in a network [@Chung1999], such that a rank of two in our partitions justifies limiting the number of communities to two.

@@

In order to evaluate the stability and topographical heterogeneity of the communities within and across subjects, we chose the adjusted rand index (ARI) as the reference metric of agreement between two clusterings [@Hubert1985]. The base of the ARI is computed by the formula

@@

Where $a$ is the number of pairs of nodes that were grouped together in both partitions, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number grouped together (separately) in one partition, but separately (together) in the other. Therefore, ARI estimates the ratio at which every pair of nodes in partition A were jointly assigned to the same/different parcels on partition B, over all possible relational changes. The resulting ratio is adjusted by comparing it to a baseline given by the expectation of a random node assignment across partitions. This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below 50%). In short, the ARI determines the chance-corrected percentage of agreement between any two partitions while being agnostic to the labeling scheme.

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns. Modularity and SP have been previously found to show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018]. Their alignment would thus give us confidence in the validity of the resulting topologies. Next, we compared the functional organization derived from the whole time series across subjects, and report the mean pairwise ARI for the group. We then performed the same evaluation for PCC and mPFC separately, and examined whether there are mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects. Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we performed all the subsequent analyses on PCC and mPFC separately.

To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the partition derived from the whole subject's data. A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017]. We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows. To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series). Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time.

We then estimated the level of agreement between network partitions estimated using data from individual days (with 2 days per participant). If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement within subject (test/re-test across days) than across subjects. We tested this idea by computing the ratio of the mean ARI within and between subjects. Ratios close to one denoted similar within-subject and across-subject alignment, whereas ratios considerably higher than one suggested that partitions were more similar within-subject than across subjects. We then extended this idea by computing the overall agreement across all runs (4 per subject) Similar to the day-based analysis, we assessed whether session-level data showed higher agreement within-subject than between subjects.

<!--
### *Estimation of Noise Effects*

BOLD signal recording through fMRI in mPFC in general, and vmPFC in particular, suffers from technical issues that promote signal dropout [@Logothetis]. Even though we made attempts to remove clear sources of noise through data preprocessing and stability analyses, it was still important to quantify the remaining potential influence of structured noise in our findings. We examined this through two complementary steps. First, we computed the temporal signal-to-noise ratio (tSNR) of all the vertices in the ROIs from the HCP minimally preprocessed data (i.e. prior to the complementary denoising described in the "fMRI Data" section). We compared the mean tSNR for each region across subjects through a permutation analysis (all permutation analyses involved 5000 iterations). In addition, we compared the mean tSNR between mPFC and PCC through a permutation analysis for each separate subject, and report the percentage of subjects who had a significantly lower mean tSNR in mPFC (post FDR correction for multiple testing [@Benjamini2001]).

Next, we examined whether a vertex's affiliation to the DMN community was driven by its tSNR. First, we computed the mean time series of each subject's DMN community. We then performed a mass univariate analysis to predict the average time series from each individual vertice's time series. The resulting $R^2$ values from each model were extracted to determine the total variance of the mean DMN time series explained by each individual vertex. If high noise in more ventral mPFC areas is affecting our results, we should see a gradient of $R^2$ values that decreases ventrally across subjects. We then spatially correlated (Pearson) each subject's $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices, and report the mean correlation across subjects. 
-->

### *Seed-based FC vs Community Detection*

We evaluated the performance of the spectral partitioning algorithm in comparison to a simpler partitioning approach using seed-based functional connectivity. First, we estimated each subject's DMN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average PCC activity for each day separately. We compared these seed-based maps with the Fiedler vectors produced by SP by spatially correlating them across days and subjects in three ways: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps. These spatial correlations were aimed to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them. The two methods were expected to produce somewhat similar arrangements, but the one displaying the higher within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018a]). We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).

@@

We performed a coordinate-based meta-analysis to identify unique standard regions across DMN and SV literatures. Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study. The 40 areas considered were limited to the medial portion of the default mode and limbic networks, as defined by the Yeo et al.'s [-@Yeo2011] 17 network parcellation. Unique areas were identified by first permuting the affiliation of each study (i.e. DMN or SV) to create a distribution of chi-squared statistics based on the comparison of the number of reports per area between literatures (see Methods for details). This putative null distribution was used to identify regions more often reported in either literature.

Figure 1 shows the proportion of times every parcel was reported in each literature, as well as the resulting significant ROIs from the permutation. The 95th percentile of the permuted chi-squared distribution was 9.11. Based on this threshold, area 7m was the only one to show unique bilateral affiliation to DMN (Left: observed $\chi^2$ = 10.07, *p* = 0.034; Right: observed $\chi^2$ = 18.89, *p* < 0.0001), while SV was uniquely represented bilaterally by area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.014; Right: observed $\chi^2$ = 12.83, *p* = 0.014). The purpose of these supra-threshold areas was to identify the most-likely affiliation of the two communities in our partitions by their coverage of these regions. However, area 25 sits in close proximity to the ventral striatum, which is reliably active in SV studies [@Bartra2013]. Considering that our projection from volumetric spheres to the cortex might have attributed striatal reports to this region, we decided not to use it as a marker of SV. We also chose not to use area v23 due to its unilateral significance (Right: observed $\chi^2$ = 11.51, *p* = 0.018). Instead, we only rely on area 7m to demarcate the DMN community.

<!--
Using each literature's mean number of reports per area as the null probability (DMN = `r BD`, 95% CI [`r BDquant`]; SV = `r BV`, 95% CI [`r BVquant`]), one-way chi-squared tests of proportions were performed to identify regions that were significantly present in their respective literatures. The resulting lists were used to identify the set of common brain areas. Unique areas were then determined by permuting the affiliation of each study (i.e. DMN or SV) to create a null distribution of chi-squared statistics, which as used to identify regions more often reported in either literature. Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.
DMN included `r length(t2)` significant regions, while SV was comprised of `r length(t1)` (see Supplemental Table 1). As expected, overlapping areas included 15 bilateral regions in PCC (31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi) (all*p*< 0.05). A region in visual cortex (V2) was also significant, but was removed due to its know unrelated function.
-->

@@

# Get the mean density for all data, daily scans, and sessions
# Check distributions, since median might be better
mdAll <- mean(Densities$Density[grep("Overall", Densities$Type)])
sddAll <- sd(Densities$Density[grep("Overall", Densities$Type)])
mdDay <- mean(Densities$Density[grep("Day", Densities$Type)])
mdSess <- mean(Densities$Density[grep("Session", Densities$Type)])
```

With these `r length(unique(str_remove(Yeo_labels, "_ROI")))` ROIs (`r (length(unique(str_remove(Yeo_labels, "_ROI"))) - 2)` overlapping, 1 DMN-specific, and 1 SV-specific), we estimated each individual's DMN coverage using their full time series (approximately 4800 total TRs from four scanning sessions over two days). Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nVertices` total vertices). After correcting for multiple comparisons, we performed spectral partitioning on these networks to identify cohesive functional communities denoting DMN and non-DMN areas. On average, networks had high densities (i.e. highly connected) regardless of whether they were produced with a single run all the full time series (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`). This high degree of density is important, as this method is known to face challenges when computed on sparse networks [@Fortunato2016].

Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning. This method dissects a network by the positive and negative values derived from the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods), which we used to binarize the ROIs. Since this is a data-driven approach, there is no a priori labeling for these communities. We thus defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (7m), and ensured that the binary labeling of the vertices was consistent across subjects. In general, the resulting pattern shows large DMN coverage in PCC, with non-DMN vertices populating its anterior segment. On the other hand, mPFC is mostly covered by DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them. This non-DMN section extends posteriorly onto pregenual cinglate cortex (area a24).

Before determining the degree of generazibility of this topological pattern across individuals, we examined the validity of these partitions by comparing them to patterns derived with a modularity algorithm [@Clauset2004]. Modularity seeks to find the pattern of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model. Since modularity is not bound to a desired number of communities, it was capable of finding more than two in our datset. We quantified the cross-method agreement with the adjusted rand index (ARI). ARI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes. This measure has the benefit of being agnostic to labeling schemes, as well as controlling for the expectation that the clusters were randomly produced [@Hubert1985]. This means that positive ARI values compare favorably against chance clustering.

>>>>

# Get the mean density for all data, daily scans, and sessions
mdAll <- mean(Densities$Density[grep("Overall", Densities$Type)])
sddAll <- sd(Densities$Density[grep("Overall", Densities$Type)])
mdDay <- mean(Densities$Density[grep("Day", Densities$Type)])
mdSess <- mean(Densities$Density[grep("Session", Densities$Type)])
```

All network analyses were performed using the igraph package [@G.2006] in R 3.4.1 [@RTeam2018]. To establish each subject's network, we selected all the vertices contained within the mPFC/PCC search space (n = 4,801 per subject; mPFC = 2854, PCC = 1947) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, in which the nodes were surface vertices and the edges were the correlations among them. Next, we applied Fisher's r to z transformation, and performed a two-sided significance test to identify strong correlations. The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were turned to 0 (all other edges retained their respective z-values). *TODO: recompute corrCounts so it also stores the # of pos/neg correlations turned to 0, as well as the number of TRs per subject (add to fMRI deets)*. Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution. Values of 1 of this transformed distribution were returned to 0 in order to avoid the inclusion of these edges in the network analyses. The proportion of remaining edges (i.e. network density) was high for all individuals(mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`). We generated and analyzed network weight matrices at four levels: 1) for each run separately (1200 TRs each); 2) for the concatenated time series for the two runs on each day (2400 TRs total); 3) for each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).

@@

Communities (i.e. clusters) were identified using the SP algorithm [@Belkin2003; @Chung1999; @Fiedler1975]. First, each network was represented as an $n$ x $n$ network weight matrix $W$ as described above (where $n$ equals the number of vertices in the search space, 4,801). This matrix was then transformed into its normalized Laplacian form

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its transformed correlation values with every other vertex), and $W$ is the network weight matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. The transformation ensures that every row sums to zero. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values and is binarized by sign [@Fiedler1975]. This method partitions the network into two similarly-sized communities, and guarantees that they share at least one edge [@Chung1999]. In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise). Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community as that which contained the DMN-specific PCC parcel identified in our meta-analysis. The high density of these networks ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].

In order to evaluate the convergent validity of the resulting partitionings across community-detection methods, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al. [-@Clauset2004]. *(TODO: rephrase) This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network. The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity.* Unlike SP, modularity can fractionate a network into more than two communities. We assumed that if the partitionings from the bounded and unbounded community detection methods showed high levels of agreement, we could gain confidence in that we were indeed fractioning the search space into an adequate number of communities. We also diagnosed our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by SP to be non-zero. This eigenvalue serves as an estimator of the optimal number of communities in a network [@Chung1999], such that a rank of two in our partitions justifies limiting the number of communities to two.

@@

In order to evaluate the stability and topographical heterogeneity of the communities within and across individuals, we chose the adjusted rand index (ARI) as a reference metric of agreement between two partitionings [@Hubert1985]. The base of the ARI is computed by the formula

@@

Where $a$ is the number of pairs of nodes that were grouped together in both partitions, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number grouped together (separately) in one partition, but separately (together) in the other. Therefore, the ARI estimates the fraction of all possible node pairs that had the same status (connected or not) in both partitionings (with the denominator equal to $(n\times (n - 1))/2$). The resulting ratio is adjusted by comparing it to a baseline given by the expectation of a random node assignment across partitions. The index ranges from 0 to 1, where 0 denotes the value expected by chance. This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below 50%). In short, the ARI determines the chance-corrected percentage of agreement between any two partitions while being agnostic to the labeling scheme.

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns. Modularity and SP have been previously found to show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018]. Alignment between the two algorithms would therefore give us confidence in the validity of the resulting partitionings. Next, we compared the partitionings derived from each individual's full time series across subjects, and report the mean pairwise ARI for the group. We then performed the same evaluation for PCC and mPFC separately, and examined whether there were mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects. Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we performed all subsequent analyses on PCC and mPFC separately.

To estimate the degree of stability of these partitions per individual we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the partition derived from the whole subject's data. A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017]. We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows. To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series). Based on this relationship, we identified a threshold Fiedler vector value for each subject, such that above-threshold vertices were persistently associated with either DMN or non-DMN more than 95% of the time.

We then estimated the level of agreement between network partitions estimated using data from individual days (with 2 days per participant). If the functional organization estimated by SP is indeed individual-specific, we should see higher agreement within individual (test/re-test across days) than across individuals. We tested this idea by computing the ratio of the mean ARI within and between individuals. Ratios close to one denoted similar within-participant and across-participant alignment, whereas ratios considerably higher than one suggested that partitions were more similar within-participant than across participants. We then extended this idea by computing the overall agreement across individual runs (4 per subject). Similar to the day-based analysis, we assessed whether run-level data showed higher agreement within-subject than between subjects.

### *Seed-based rsFC versus Community Detection*

We evaluated the performance of the SP algorithm in comparison to a simpler partitioning approach using seed-based functional connectivity. First, we estimated each subject's DMN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average activity across all vertices in PCC for each day separately. We compared these seed-based maps with the Fiedler vectors produced by SP by examining three sets of spatial correlations across vertices between days: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps. These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them. The two methods were expected to produce somewhat similar results, but the one displaying greater within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018a]). We therefore compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).

@@

We performed a coordinate-based meta-analysis to identify subregions of mPFC and PCC that were preferentially associated with the DMN or SV literatures. Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to discrete parcels from a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study. The `r length(Yeo_labels)` parcels considered were limited to the medial portion of the default mode and limbic networks defined by the Yeo et al.'s [-@Yeo2011] 17-network parcellation. Unique areas were identified by first permuting the domain labels across studies (DMN or SV) to create a null distribution for the maximum chi-squared statistic in the search space (see Methods for details). The null distribution was used to identify regions that were reported significantly more often reported in one literature or the other.

Figure 1 shows the proportion of times every parcel was reported in each literature, as well as the significant differences between domains. The 95th percentile of the permuted chi-squared distribution was 9.11. Based on this threshold, area 7m in PCC/precuneus was the only parcel to show a preferential affiliation to DMN bilaterally (Left: observed $\chi^2$ = 10.07, *p* = 0.034; Right: observed $\chi^2$ = 18.89, *p* < 0.0001). The adjacent area v23 exhibited a similar effect, albeit only unilaterally (Right: observed $\chi^2$ = 11.51, *p* = 0.018; **TODO: ADD LEFT**). There appeared to be a bilateral preference toward valuation effects in area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.014; Right: observed $\chi^2$ = 12.83, *p* = 0.014); however, closer inspection suggested this effect was driven by subcortical foci centered in adjacent ventral striatum. No toher parcels were preferentially implicated in valuation relative to DMN. We therefore selected area 7m as an interpretable, bilateral reference point for labeling DMN and non-DMN communities in the analyses that follow. We note that area 7m has been found to not partake in DMN in previous work [@AndrewsHanna2010]. However, we adhere to the nomenclature established by [@Glasser2016], whose area 7m is positioned considerably more ventrally and is well contained within canonical DMN.

@@

With our mPFC/PCC search space, we estimated each individual's DMN coverage using their full time series (approximately 4800 total TRs from four scanning sessions over two days). Each subject's network (n = `r nSubj`) was constructed by calculating pairwise correlations among the time series for all the surface vertices in the search space (`r nVertices` total vertices). We applied the SP community detection algorithm to thresholded transformations of these networks to identify cohesive functional communities corresponding to DMN and non-DMN areas.

Figure 2 shows a representative partitioning of the search space for a single participant (100307). The SP algorithm subdivides a network according to the positive versus negative values in the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods). Since this is a data-driven approach, there is no a priori labeling for the two communities. We thus defined the DMN community as the one containing the one DMN-specific PCC parcel from the meta-analysis (7m). In qualitative terms, the resulting patterns contained substantial DMN coverage in posterior PCC (as dictated by our labeling strategy), with non-DMN vertices in anterior PCC. The mPFC region tended to include DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them. This non-DMN section extended posteriorly into pregenual cinglate cortex (area a24).

Before evaluating the degree of generazibility of this topological pattern across individuals, we examined the validity of these partitions by comparing them to patterns derived with a modularity algorithm [@Clauset2004]. Modularity seeks to find the pattern of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model. Since modularity is not bound to a desired number of communities, it was capable of finding more than two in our datset. We quantified the cross-method agreement with the adjusted rand index (ARI). ARI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes. This measure has the benefit of being agnostic to labeling schemes, as well as controlling for the expectation that the clusters were randomly produced [@Hubert1985]. This means that positive ARI values compare favorably against chance clustering.
